|

### 2024-08-09 doc/paper.qmd
do analysis

### Smoothing Reported Operating Earnings Using Accruals (EM1)
`EM1` is a measure that assesses how much insiders (e.g., company executives) smooth or stabilize reported earnings by manipulating accruals. The concept is that firms may attempt to reduce fluctuations in their reported operating income to present a more stable financial performance to investors. This measure reflects the degree to which insiders use accounting discretion to smooth reported earnings, with lower values of EM1 suggesting more aggressive earnings smoothing.

@@

$$
\begin{aligned}
\text{Accruals}_{it} &= (\Delta \text{CA}_{it} - \Delta \text{Cash}_{it}) - (\Delta \text{CL}_{it} - \Delta \text{STD}_{it} - \Delta \text{TP}_{it}) - \text{Dep}_{it} 
& \\
\text{where:} \\
\Delta \text{CA}_{it} & = \text{Change in total current assets} \\
\Delta \text{Cash}_{it} & = \text{Change in cash and cash equivalents} \\
\Delta \text{CL}_{it} & = \text{Change in total current liabilities} \\
\Delta \text{STD}_{it} & = \text{Change in short-term debt included in current liabilities} \\
\Delta \text{TP}_{it} & = \text{Change in income taxes payable} \\
\text{Dep}_{it} & = \text{Depreciation and amortization expense}
\end{aligned}
$$

>>>>

### Smoothing Reported Operating Earnings Using Accruals (EM1)
`EM1` is a measure that assesses how much insiders (e.g., company executives) smooth or stabilize reported earnings by manipulating accruals. The concept is that firms may attempt to reduce fluctuations in their reported operating income to present a more stable financial performance to investors. This measure reflects the degree to which insiders use accounting discretion to smooth reported earnings, with lower values of EM1 suggesting more extensive earnings smoothing.

@@

$$
\begin{aligned}
\text{Accruals}_{it} &= (\Delta \text{CA}_{it} - \Delta \text{Cash}_{it}) - (\Delta \text{CL}_{it} - \Delta \text{STD}_{it} - \Delta \text{TP}_{it}) - \text{Dep}_{it} 
& \\
\text{where:} \\
\Delta \text{CA}_{it} & = \text{Change in total current assets} \\
\Delta \text{Cash}_{it} & = \text{Change in cash and cash equivalents} \\
\Delta \text{CL}_{it} & = \text{Change in total current liabilities} \\
\Delta \text{STD}_{it} & = \text{Change in short-term debt included in current liabilities} \\
\Delta \text{TP}_{it} & = \text{Change in income taxes payable} \\
\text{Dep}_{it} & = \text{Depreciation and amortization expense for firm i in year t} 
\end{aligned}
$$
